A Monte Carlo based new sampling calorimeter toward the measurement of $\gamma$ incident angle

### 2021-07-30 paper.tex
updates

\subsection{Detector dimension}
The performance of the detector is tested with different detector dimensions. Different geometries are simulated in the Geant4 package and corresponding training procedures are applied with the same number of training events as 100,000. It if found that the configuration with 15-mm-wide strips provides better resolution than one with smaller strip widths.

The angle reconstruction is tested only with signals in front layers. Usages of front-layer signals are applied to the data sample for training and test procedures at the same time. The reconstruction with 24 layers, which possess the 4.6$X_{0}$, provides identical resolution with one from full geometry, while possessing about xxx\% inefficiency due to no responses in the front region. As a results of the inefficiency, A delta peak can be seen in Fig.(fl). This peak can be rejected with the application of the total energy threshold (10~MeV in Fig.(fl)) in the front region.

>>>>

\subsection{Detector dimension}
\begin{figure}[!hbt]
\includegraphics[width=0.58\textwidth]{figures/Fig2_reco_Width_width.pdf}
\caption{ The angular resolution as a function of the scintillator strip width for 1 GeV $\gamma$. The incident angle for each simulation is fixed as 10 degree.  }
\label{fig:angle_reco_width}
\end{figure}

The performance of the detector is tested with different detector dimensions. Different geometries are simulated in the Geant4 package and corresponding training procedures are applied with the same number of training events as 100,000. Figure~\ref{fig:angle_reco_width} shows the angular resolution of the reconstruction as a function of the scintillator strip width with the 5-mm step. It if found that the configuration with 15-mm-wide strips provides better resolution than one with smaller strip widths, and the configuration with larger strip size than 15 mm does not provide improved resolution. Based on this, The width of the strip is determined to be 15 mm.

\begin{figure}[!hbt]
\includegraphics[width=0.48\textwidth]{figures/Fig3_reco_layer_hist.pdf}
\includegraphics[width=0.48\textwidth]{figures/Fig3_reco_layer_graph.pdf}
\caption{ (Color online) Reconstructed $\theta$ for 1 GeV and $\theta_{\rm{true}}=$~10~deg $\gamma$ with (red) and without (black) the total energy ($E_{\rm{tot}}$) selection (left), and the angular resolution as a function of front layer depth used for the reconstruction (right). The inefficiency for 4.6$X_{0}$ is estimated to be 5.8\%  }
\label{fig:angle_reco_layer}
\end{figure}

The angle reconstruction is tested only with signals in front layers. Usages of front-layer signals are applied to the data sample for training and test procedures at the same time. The reconstruction with 24 layers, which possess the 4.6$X_{0}$, provides the identical resolution with one from full geometry. The inefficiency can arise mainly due to no responses in the front region, and can be evaluated by comparing the number of events with and without applying the minimum total energy ($E_{\rm{tot}}$) threshold in the front region. The inefficiency for (4.6$X_{0}$) is estimated to be 5.8\%. Figure~\ref{fig:angle_reco_layer} shows the reconstructed $\theta$ distribution (left) and the angular resolution as a function of front layer depth used for the reconstruction (right). The reconstructed $\theta$ without the $E_{\rm{tot}}$ threshold exhibits a delta peak near $\theta=$~0 as a results of not enough information to reconstruct $\theta$, And this peak clearly disappears by applying the $E_{\rm{tot}}$ threshold. The angular resolution is evaluated after applying the $E_{\rm{tot}}$ threshold and estimated to be 1.3 deg, which is comparable results with fig.~\ref{fig:angle_reco_width} for 4.6$X_{0}$ depth, so that the radiation length for the $\theta$ reconstruction is determined to be 4.6$X_{0}$.
